The markings of the trade: exploring the patterns of olive oil production in Roman Baetica

### 2020-03-25 Paper/jaccardbaetica.tex
add germania part

This fact seems to concur with the latest research that reinforce the idea of a more important Atlantic route that would connect the provinces militarized.

(Remesal Rodrı́guez, 1986; 2008; Carreras Monfort y Morais, 2012; Morillo
et al., 2016; Rubio-Campillo et al., 2018b).

>>>>

This fact seems to concur with the latest research that suggest the idea of a more important Atlantic route that would connect the provinces militarised\citep{remesal_annona_1986,
remesal_provincial_2008,
carreras_atlantic_2012,
morillo_hispania_2016,rubio-campillo_provincias_2018}.

Therefore, most part of the centres where similar stamps are shared can correspond to eminently military areas, which may mean that the transport could reach the military areas from the beginning and then be distributed by land routes along other civil areas \citep{carreras_britannia_1998,
ayllon_olive_2018}.

In \textit{Germania}, the results followed the same pattern than Britannia but with a minor correlation as we can observed in the dendrogram. The areas mostly militarised share similar stamps than civil areas. However, we do not detect a concrete pattern regarding the distribution of the stamps in the german limes. \maria{citar remesal xanten}.

It is worth to know that it was not detected a robust model of organisation in both cases with regard to the distribution of stamps in consumption centres. This means
that it is unknown whether certain production centres went to one province or another or, at the
less, that it can be clearly reflected in the data with a greater similarity in the amphoric stamps. Thus, production centres could have distributed randomly olive oil both \textit{Britannia} and \textit{Germania}. We do not detect production centres dedicated to the distribution of olive oil in a certain province.

In general, we observed a distribution of the stamps to military stamps. By contrast, judging by the results obtained, there does not seem to be a specific pattern in terms of geographical distribution. Nor it was detected consumption areas where stamps are specified from a amphora workshop.
